---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# preprivalry

<!-- badges: start -->
[![Travis build status](https://travis-ci.com/cemreyilmaz/preprivalry.svg?branch=master)](https://travis-ci.com/cemreyilmaz/preprivalry)
<!-- badges: end -->

The goal of preprivalry is the preprocessing of binocular rivalry data
which are collected via PsychToolbox in MATLAB environment in the project by 
NeuroVision research group in the University of Graz. A rivalry data-set can be 
analyzed by using this package if it is organized as required.

## Installation

You can install the released version of preprivalry from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("preprivalry")
```
## Data structure

Since our data were collected on MATLAB, this package includes some functions to
reorganize the data.

#### MATLAB data

Our .mat file includes a MATLAB structure named as log. Besides the other 
variable, its forth component is a struct containing the key events and fifth 
component is a struct containing the experiment info, as the following:

```
raw_data
  --raw_data.key
    --raw_data.key.perceptKeys  # key codes of instructed keys  [key_1, key_2]
    --raw_data.key.perceptNames # key names of instructed keys  {key_1, key_2}
    --raw_data.key.idDown       # key codes of pressed keys     [nx1 double]
    --raw_data.key.timeDown     # time points for pressed keys  [nx1 double]
    --raw_data.key.idUp         # key codes of released keys    [nx1 double]
    --raw_data.key.timeUp       # time points for released keys [nx1 double]
  --raw_data.exp
    --raw_data.exp.trialStartTime # [trial_1, trial_2]
    --raw_data.exp.trialEndTime   # [trial_1, trial_2]
```

We saved separate .mat files for each experimental run by naming the file as:
ExperimentName_s###_session#_run#_date.mat

## Example

The subject data can be preprocessed by using only one function:

```{r example}
library(preprivalry)
## basic example for preprocessing of subject data
directory <- paste(getwd(), '/tests', sep='')
exp_list <- c('RivalryGratings','RivalryImages')
subj <- 's001'
ses <- 1
data <- preprocessing_subject(directory,exp_list,subj,ses)
```

The output can be saved also as an excel file as following:
```{r csv}
library(preprivalry)
## basic example for saving as csv
directory <- paste(getwd(), '/tests',sep='')
output_file <- paste(directory, '/data.csv', sep='')
exp_list <- c('RivalryGratings','RivalryImages')
subj <- 's001'
ses <- 1
raw_data <- read_rivdata(directory,exp_list[1],subj,'session1')
percept_keys <- rbind(raw_data[["log"]][[4]][[1]],
                      c(raw_data[["log"]][[4]][[2]][[1]][[1]],raw_data[["log"]][[4]][[2]][[2]][[1]]))
data <- preprocessing_subject(directory,exp_list,subj,ses)
data <- reorganize_as_table(data)
```

Check the function file preprivalry_preprocessing_data.R to see more details and to customize the workflow. For example, you can reorganize the trial data and use it for further analysis by using the key events and trial info:

```{r trial}
library(preprivalry)
## basic example for preprocessing of trial data
idUp <- c(39,39,37,37,39,37)
timeUp <- c(16412818,16412831,16412841,16412846,16412852,16412857)
idDown <- c(39,39,37,37,39,37)
timeDown <- c(16412817,16412825,16412834,16412844,16412847,16412854)
exp_key <- data.frame(idUp,timeUp,idDown,timeDown)
trialStartTime <- c(16412816,16412843)
trialEndTime <- c(16412842,16412859)
exp <- data.frame(trialStartTime,trialEndTime)
trial_key <- extract_trialkey(exp_key,exp[1,])
trial_key <- clean_keyevents(trial_key,2)
data <- reorganize_preptrial(trial_key,exp[1,])
```
