---
title: "Descriptive Statistics"
author: "Cemre Yilmaz"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Preprocessing with preprivalry}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(preprivalry)
```

The package **preprivalry** has a couple of functions for basic statistics on rivalry. The descriptives can be calcuated for eye (```descriptive_eye()```) and for percept (```descriptive_trial()```). The structures of input and output are the same for both functions. Just remember that they calculate the descriptives for all the given data. So, if you want descriptives for trial 1 of experiment 1 in session 1, you need to extract the data first.

```{r stats}
load(paste0(getwd(),"/data/sample_data.Rdata"))
stats     <- descriptive_trial(rivalry_data[rivalry_data$trial == 1 & rivalry_data$run == 1,])
stats
stats_eye <- descriptive_eye(rivalry_data[rivalry_data$trial == 1 & rivalry_data$run == 1,])
stats_eye
```

