---
title: "Exclusion Criteria"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Exclusion-Criteria}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(preprivalry)
```
If the participants have a strong eye dominance or they responded very unreliably, their data are misleading for our purposes. Therefore, we exclude such cases. 

## Eye dominance

We calculate eye dominance by ```rivalry.eye.dominance()``` just after the first session, and if the value is higher than 0.8, we stop the experiments with that subject. 

```{r eyeDominance}
load(paste0(getwd(),"/data/sample_data.Rdata"))
rivalry.eye_dominance(rivalry_data)
```
## Replay score

We calculate the ratio of correct response of subject in each run and average these scores. This is the replay score of a subject and it is expected to be higher than 0.5. 

```{r replayScore}
load(paste0(getwd(),"/data/sample_data.Rdata"))
repdata <- preprivalry::rescale_replay_data(repdata)
replay_score(repdata)
```
