---
title: "MATLAB to R"
author: "Cemre Yilmaz"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{matlab_to_r}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(preprivalry)
```


Since our data were collected on MATLAB, the package **preprivalry** includes some functions to reorganize the data.

# Data structure

Our .mat file includes a MATLAB structure named as "log". Besides the other variables, its forth component is a struct containing the key events and fifth component is a struct containing the experiment info, as the following:

```
log
  --log.key
    --log.key.perceptKeys  # key codes of instructed keys  [key_1, key_2]
    --log.key.perceptNames # key names of instructed keys  {key_1, key_2}
    --log.key.idDown       # key codes of pressed keys     [nx1 double]
    --log.key.timeDown     # time points for pressed keys  [nx1 double]
    --log.key.idUp         # key codes of released keys    [nx1 double]
    --log.key.timeUp       # time points for released keys [nx1 double]
  --log.exp
    --log.exp.trialStartTime # [trial_1, trial_2]
    --log.exp.trialEndTime   # [trial_1, trial_2]
```

## Import the data from a .mat file
One can import the data by using ```read_rivdata()``` function.

We saved separate .mat files for each experimental run by naming the file as: ExperimentName_s###_session#_run#_date.mat. Therefore, the function first creates the full path. Then, it checks if the file exists. If it exits, the function reads it. If an error comes up, it warns the user.


```{r importingData}
setwd("..")
directory <- paste0(getwd(),"/data") # the folder which contains the data
s         <- 1 # session number 
data      <- read_rivdata(directory,"Gratings","s001",s)
summary(data)

```

Our interest will be on ```data[["log"]]``` for the further steps.
