---
title: "Preprocessing of a Run"
author: "Cemre Yilmaz"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{preprocessing_run}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(preprivalry)
```

After importing the data from a .mat file, we have a list containing all the information about the given run. Now, we need to do preprocessing.

First, we extract the basic info and create a data.frame such that:
```
trial_info
  --trialStartTime (tx2 matrix)
  --trialEndTime   (tx2 matrix)
```
where t is the number of trials by using ```extract_exp()```. Then, we create a list containing the key events during the given run. We use ```extract_key()``` and the output is a data.frame like that:
```
key
  --nameKeyRelease
  --idKeyRelease
  --timeKeyRelease
  --nameKeyPress
  --idKeyPress
  --timeKeyPress
```
Since we preprocess the data trial by trial, we use ```extract_trialkey()``` to get the key events during the given trial. Then, we remove the key events other than the perceptual reports (```remove_irrelevant_keyevents()```) followed by cleaning the key events (```clean_keyevents()```) including: 
    removal of first event 
        if key release comes before first key press
        if key release and key press are not of the same percept at the beginning
   removal of last key press if last key press comes after last key release
   removal of last key event if key release and key press are not of the same percept at the end
   correct any mismatch between key releases and key presses

After that, ```preprocessing_trial()``` organizes the data and ```create_transitionkey()``` creates the timing info of transitions for further analysis. 

If there is no key events were recorded during the given trial, ```create_nan_trialdata()``` creates same data.frame with nans. 

All these preprocessing steps will be performed for a run by ```preprocessing_run()``` function. As a final step, we add the info for dominant eye. ```eye_info()``` adds the dominant eye as a new field to the data.
```
directory <- "/data" # the folder which contains the data
run_data <- preprivalry::preprocessing_run(directory,"Gratings","s001",1)
```
```{r, include = FALSE}
load(paste0(getwd(),"/data/sample_data.Rdata"))
```
```{r preprocessingrun}
run_data <- preprivalry::eye_info(run_data)
head(run_data,1) # data of trial 1
```
