---
title: "Routine Preprocessing"
author: "Cemre Yilmaz"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{routine_preprocessing}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(preprivalry)
```
**preprivalry** includes ```preprocessing_session()``` and ```preprocessing_subject()``` to preform preprocessing. ```preprocessing_session()``` runs ```preprocessing_run()``` followed by ```eye_info()``` to get a clean data for given experiments. ```preprocessing_subject()``` runs ```preprocessing_session()``` for the given sessions and saves the name of percept keys in addition to the previous preprocessing steps. The data can be converted into data.frame for easier view and use by using ```reorganize_as_table()``` after ```preprocessing_subject()```.

After data collection, one can complete preprocessing with a few line:

```
directory <- "/data" # the folder which contains the data
experiments <- c("Gratings","Images","GratingImage") 
subjects <- c("s001","s002","s003")
sessions <- 3 # total number of sessions
rivalry_data <- c()
for(s in subjects){
  data <- preprocessing_subject(directory,experiments,s,sessions)
  data <- reorganize_as_table(data)
  if(length(rivalry_data)==0){
    rivalry_data <- data
  } else{
    rivalry_data <- rbind(rivalry_data,data)
  }
}
```
```{r, include=FALSE}
load(paste0(getwd(),"/data/sample_data.Rdata"))
```
```{r preprocessing}
head(rivalry_data)
```
